---
title: "Descriptive Stats, Feature Selection, Estimates and Interpretations"
author: "Nicholas Paschall"
date: '2023-05-17'
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
set.seed(1234)

library(readr)
library(tidyverse)
library(caret)
library(glmnet)
library(ggplot2)
library(RColorBrewer)
library(leaps)
library(bestglm)
library(boot)
library(ggcorrplot)
library(hrbrthemes)
library(rlang)
library(e1071)
library(MASS)
library(pROC)
library(dplyr)
library(gridExtra)

setwd("~/Documents/STSCI 4100")
combo.df <- read_csv("combo.df.csv")[,c(6:13, 17:24, 28, 27)]
```

# **Descriptive Statistics**

## *Summaries*
```{r}
length( which(combo.df$draft.fac==1) )
length( which(combo.df$draft.fac==0) )
nrow( combo.df )
```
### Ht
```{r}
summary(combo.df$Ht)[c(1,3,6)]
sd(combo.df$Ht)
summary(glm(draft.fac~Ht, data=combo.df, family=binomial))$coefficients[2,4]
ht.hist <- ggplot(combo.df, aes(x = cut(Ht, breaks=c(5, 6.1, 6.2, 6.3, 6.6)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Height", title="Ht", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
ht.hist
```
### Wt
```{r}
summary(combo.df$Wt)[c(1,3,6)]
sd(combo.df$Wt)
summary(glm(draft.fac~Wt, data=combo.df, family=binomial))$coefficients[2,4]
wt.hist <- ggplot(combo.df, aes(x = cut(Wt, breaks=c(201, 233, 238, 245, 260)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Weight", title="Wt", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
wt.hist
```
### forty_yd
```{r}
summary(combo.df$forty_yd)[c(1,3,6)]
sd(combo.df$forty_yd)
summary(glm(draft.fac~forty_yd, data=combo.df, family=binomial))$coefficients[2,4]
forty_yd.hist <- ggplot(combo.df, aes(x = cut(forty_yd, breaks=c(4.37, 4.62, 4.72, 4.81, 5.09)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Forty Yard Dash", title="forty_yd", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
forty_yd.hist
```
### vertical
```{r}
summary(combo.df$vertical)[c(1,3,6)]
sd(combo.df$vertical)
summary(glm(draft.fac~vertical, data=combo.df, family=binomial))$coefficients[2,4]
vertical.hist <- ggplot(combo.df, aes(x = cut(vertical, breaks=c(26, 31.5, 33, 35, 43)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Vertical Jump", title="vertical", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
vertical.hist
```
### bench
```{r}
summary(combo.df$bench)[c(1,3,6)]
sd(combo.df$bench)
summary(glm(draft.fac~bench, data=combo.df, family=binomial))$coefficients[2,4]
bench.hist <- ggplot(combo.df, aes(x = cut(bench, breaks=c(10, 19, 21, 24, 36)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Bench Press", title="bench", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
bench.hist
```
### broad_jump
```{r}
summary(combo.df$broad_jump)[c(1,3,6)]
sd(combo.df$broad_jump)
summary(glm(draft.fac~broad_jump, data=combo.df, family=binomial))$coefficients[2,4]
broad_jump.hist <- ggplot(combo.df, aes(x = cut(broad_jump, breaks=c(103, 115, 118, 122, 140)), 
                    fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Broad Jump", title="broad_jump", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
broad_jump.hist
```
### cone
```{r}
summary(combo.df$cone)[c(1,3,6)]
sd(combo.df$cone)
summary(glm(draft.fac~cone, data=combo.df, family=binomial))$coefficients[2,4]
cone.hist <- ggplot(combo.df, aes(x = cut(cone, breaks=c(6.63, 7.02, 7.14, 7.26, 7.87)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Cone Time", title="cone", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
cone.hist
```
### shuttle
```{r}
summary(combo.df$shuttle)[c(1,3,6)]
sd(combo.df$shuttle)
summary(glm(draft.fac~shuttle, data=combo.df, family=binomial))$coefficients[2,4]
shuttle.hist <- ggplot(combo.df, aes(x = cut(shuttle, breaks=c(3.99, 4.26, 4.33, 4.39, 4.97)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Shuttle", title="shuttle", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
shuttle.hist
```
### tackles_solo
```{r}
summary(combo.df$tackles_solo)[c(1,3,6)]
sd(combo.df$tackles_solo)
summary(glm(draft.fac~tackles_solo, data=combo.df, family=binomial))$coefficients[2,4]
tackles_solo.hist <- ggplot(combo.df, aes(x = cut(tackles_solo, breaks=c(5.9, 83, 117.5, 151, 339)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Solo Tackles", title="tackles_solo", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
tackles_solo.hist
```
### tackles_ast
```{r}
summary(combo.df$tackles_ast)[c(1,3,6)]
sd(combo.df$tackles_ast)
summary(glm(draft.fac~tackles_ast, data=combo.df, family=binomial))$coefficients[2,4]
tackles_ast.hist <- ggplot(combo.df, aes(x = cut(tackles_ast, breaks=c(1, 57, 92, 117, 211, 311)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Assisted Tackles", title="tackles_ast", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
tackles_ast.hist
```
### tackles_tot
```{r}
summary(combo.df$tackles_tot)[c(1,3,6)]
sd(combo.df$tackles_tot)
summary(glm(draft.fac~tackles_tot, data=combo.df, family=binomial))$coefficients[2,4]
tackles_tot.hist <- ggplot(combo.df, aes(x = cut(tackles_tot, breaks=c(7, 144, 210.5, 267, 633.5)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Total Tackles", title="tackles_tot", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
tackles_tot.hist
```
### tackles_loss
```{r}
summary(combo.df$tackles_loss)[c(1,3,6)]
sd(combo.df$tackles_loss)
summary(glm(draft.fac~tackles_loss, data=combo.df, family=binomial))$coefficients[2,4]
tackles_loss.hist <- ggplot(combo.df, aes(x = cut(tackles_loss, breaks=c(-1, 16, 22.5, 29.125, 75)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Tackles for Loss", title="tackles_loss", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
tackles_loss.hist
```
### sacks
```{r}
summary(combo.df$sacks)[c(1,3,6)]
sd(combo.df$sacks)
summary(glm(draft.fac~sacks, data=combo.df, family=binomial))$coefficients[2,4]
sacks.hist <- ggplot(combo.df, aes(x = cut(sacks, breaks=c(-1, 4.5, 7, 12, 38)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Sacks", title="sacks", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
sacks.hist
```
### def_int
```{r}
summary(combo.df$def_int)[c(1,3,6)]
sd(combo.df$def_int)
summary(glm(draft.fac~def_int, data=combo.df, family=binomial))$coefficients[2,4]
def_int.hist <- ggplot(combo.df, aes(x = cut(def_int, breaks=c(-1, 1, 3, 15)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Defensive Interceptions", title="def_int", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
def_int.hist
```
### pass_defended
```{r}
summary(combo.df$pass_defended)[c(1,3,6)]
sd(combo.df$pass_defended)
summary(glm(draft.fac~pass_defended, data=combo.df, family=binomial))$coefficients[2,4]
pass_defended.hist <- ggplot(combo.df, aes(x = cut(pass_defended, breaks=c(-1, 3, 5, 8, 27)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Passes Defended", title="pass_defended", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
pass_defended.hist
```
### forced_fumble
```{r}
summary(combo.df$forced_fumble)[c(1,3,6)]
sd(combo.df$forced_fumble)
summary(glm(draft.fac~forced_fumble, data=combo.df, family=binomial))$coefficients[2,4]
forced_fumble.hist <- ggplot(combo.df, aes(x = cut(forced_fumble, breaks=c(-1, 1, 2, 4, 16)), 
                     fill = factor(draft.fac)))+ 
    geom_bar(position = "fill") +
    stat_count(geom = "text", 
               aes(label=..count..), 
               position = position_fill(vjust = 0.5), size=7) +
    theme_light() + 
    labs(y="Proportion", x="Forced Fumbles", title="forced_fumble", fill="Draft Status") + 
    theme(panel.grid.minor=element_blank(), legend.position = "bottom",
          axis.text.x=element_text(size=15), plot.title=element_text(size=17), 
          plot.subtitle=element_text(size=14), axis.title.x=element_text(size=14), 
          legend.text=element_text(size=14), legend.title=element_text(size=14),
          axis.title.y=element_text(size=14), axis.text.y=element_text(size=15) )
forced_fumble.hist
```

\newpage 

# **Feature Selection**

## *Data Preparation*
```{r}
set.seed(1234)
# standardization
x <- scale(combo.df[1:16])
y <- combo.df$draft.fac
year <- combo.df$year
combo.df <- as.data.frame( cbind(x, y, year) ) %>%
    rename(draft.fac = y)

# Upsampling for Unrepresented Class (Undrafted Players)
draft.fac.factor <- as.factor( combo.df$draft.fac )
prop.table( table( draft.fac.factor ) ) # very disproportionate classes

predictor.df <- combo.df[ , c(1:16, 18) ]
combo.df <- upSample( x=predictor.df, y=draft.fac.factor ) %>%
    rename( draft.fac=Class )
table( combo.df$draft.fac ) # proportionate classes 

combo.df$draft.fac <- as.numeric( as.character( combo.df$draft.fac ) )

# box plots of combine statistic variables
ggplot( data=combo.df ) +
    geom_boxplot( aes(x="forty_yd", y=forty_yd), fill = brewer.pal(12, "Set3")[1] ) +
    geom_boxplot( aes(x="vertical", y=vertical), fill = brewer.pal(12, "Set3")[2] ) +
    geom_boxplot( aes(x="broad_jump", y=broad_jump), fill = brewer.pal(12, "Set3")[3] ) +
    geom_boxplot( aes(x="bench", y=bench), fill = brewer.pal(12, "Set3")[4] ) +
    geom_boxplot( aes(x="shuttle", y=shuttle), fill = brewer.pal(12, "Set3")[5] ) +
    geom_boxplot( aes(x="cone", y=cone), fill = brewer.pal(12, "Set3")[6] ) +
    theme_light() + labs(title="Combine Variables") +
    theme(axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 45, hjust = 1, size=15),
          axis.text.y = element_text(size=15), plot.title=element_text( size=17))

# box plots of career statistic variables
ggplot( data=combo.df ) +
    geom_boxplot( aes(x="tackles_solo", y=tackles_solo), fill=brewer.pal(12, "Set3")[1] ) +
    geom_boxplot( aes(x="tackles_ast", y=tackles_ast), fill=brewer.pal(12, "Set3")[2] ) +
    geom_boxplot( aes(x="tackles_tot", y=tackles_tot), fill=brewer.pal(12, "Set3")[3] ) +
    geom_boxplot( aes(x="tackles_loss", y=tackles_loss), fill=brewer.pal(12, "Set3")[4] ) +
    geom_boxplot( aes(x="sacks", y=sacks), fill=brewer.pal(12, "Set3")[5] ) +
    geom_boxplot( aes(x="def_int", y=def_int), fill=brewer.pal(12, "Set3")[6] ) +
    geom_boxplot( aes(x="pass_defended", y=pass_defended), fill=brewer.pal(12, "Set3")[7] ) +
    geom_boxplot( aes(x="forced_fumble", y=forced_fumble), fill=brewer.pal(12, "Set3")[8] ) +
    theme_light() + labs(title="Career Variables") +
    theme(axis.title.x = element_blank(), axis.title.y = element_blank(), 
          axis.text.x = element_text(angle = 45, hjust = 1, size=15),
          axis.text.y = element_text(size=15), plot.title=element_text( size=17))
```

## *Correlation Matrices*
```{r}
# combine correlation matrix
combine.mat <- as.matrix( combo.df[ ,c(1:8, 18) ] )
combine.corr <- round( cor( combine.mat ), 1 )
ggcorrplot( combine.corr, lab=TRUE ) +
    ggtitle( "Combine Measurements" ) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.x = element_blank(), axis.title.y = element_blank())

# career stats correlation matrix
career.mat <- as.matrix( combo.df[ ,c(9:16,18) ] )
career.corr <- round( cor( career.mat ), 1 )
ggcorrplot( career.corr, lab=TRUE ) +
    ggtitle( "Career Measurements" ) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title.x = element_blank(), axis.title.y = element_blank()) 

full.mat <- as.matrix( combo.df[ ,c( 1:17 ) ] )
full.corr <- round( cor( full.mat ), 1 )
ggcorrplot( full.corr, lab=TRUE )
```

## *Best Subset Selection*
```{r}
set.seed(1234)
draft.glm <- combo.df %>%
    rename( y = draft.fac ) %>% dplyr::select( -year, -tackles_tot ) # get rid of tackles_tot due to multicollinearity

# best subset based off AIC
best.sub.AIC <- bestglm( draft.glm,
                         family=binomial,
                         method="exhaustive",
                         IC="AIC" )
# best subset based off BIC
best.sub.BIC <- bestglm( draft.glm,
                         family=binomial,
                         method="exhaustive",
                         IC="BIC" )

# creates dataframe for each model and calculates McFadden R^2 and deviance
model.stats <- function( covariates ){
    df <- data.frame( model = rep( NA, times=length( covariates ) ) )
    
    for( i in 1:length(covariates) ){
        if( i ==1 ){
            tmp.formula <- "draft.fac ~ 1"
            mod <- glm( tmp.formula, data=combo.df, family="binomial" )
        }else{
            tmp.formula <- paste( covariates[ as.matrix( best.sub.AIC$Subsets[i, 1:16] )], collapse=" + " )
            tmp.formula <- paste( "draft.fac ~", tmp.formula )
            mod <- glm( tmp.formula, data=combo.df, family="binomial" )
        }
        df$mcfad.R[i] <- 1 - logLik(mod) / logLik( glm(draft.fac~1, data=combo.df, family="binomial") )
        df$dev[i] <- mod$deviance
        df$model[i] <- tmp.formula
    }
    return( df )
}

covariates <- colnames( best.sub.AIC$Subsets[, 1:16 ] )
covariates[1] <- "1"
glm.model.stats <- model.stats(covariates)
glm.model.stats$aic <- best.sub.AIC$Subsets$AIC
glm.model.stats$bic <- best.sub.BIC$Subsets$BIC

head( glm.model.stats, n=10 )


# Deviance Plot for Each Model
ggplot( data = glm.model.stats, aes(x=1:16, y=dev, label=round(dev, 1) ) ) +
    geom_point() +
    geom_path(alpha=0.3) +
    theme_light() + scale_x_continuous( n.breaks=16 ) +
    scale_y_continuous( n.breaks=10 ) +
    labs( y="Deviance", x="Model Number", title="Model Deviances") +
    geom_text( size=2.5, vjust= -0.75 ) +
    theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15),
          plot.title=element_text(size=17), axis.title.x=element_text(size=13),
          axis.title.y=element_text(size=13))

# McFadden R-Squared Values for Each Model
mcfad <- ggplot( data = glm.model.stats, aes(x=1:16, y=mcfad.R, label=round(mcfad.R, 2) ) ) +
    geom_point() +
    geom_path(alpha=0.3) +
    theme_light() + scale_x_continuous( n.breaks=9 ) +
    scale_y_continuous( n.breaks = 10 ) +
    labs( y="McFadden R-Squared", x="Model Number", title="McFadden R^2" ) +
    #geom_text( size=2.5, vjust=-0.75 ) +
    theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15),
          plot.title=element_text(size=17), axis.title.x=element_text(size=13),
          axis.title.y=element_text(size=13))

# AIC/BIC Values for Each Model
aicbicdev <- ggplot( data = glm.model.stats ) +
    geom_point( aes(x=1:16, y=aic, color="AIC") ) +
    geom_path( aes(x=1:16, y=aic, color="AIC"), alpha=1 ) +
    #geom_text( aes(x=1:16, y=aic, label=round(aic, 1) ), size=2.5, vjust=-0.75 ) +
    geom_point( aes(x=1:16, y=bic, color="BIC") ) +
    geom_path( aes(x=1:16, y=bic, color="BIC"), alpha=1 ) +
    #geom_text( aes(x=1:16, y=bic, label=round(bic, 1) ), size=2.5, vjust=-0.75 ) +
    geom_point( aes(x=1:16, y=dev, color="Deviance") ) +
    geom_path( aes(x=1:16, y=dev, color="Deviance"), alpha=1 ) +
    #geom_text( aes(x=1:16, y=dev, label=round(dev, 1) ), size=2.5, vjust=-0.75) +
    theme_light() + scale_y_continuous(n.breaks = 10) +
    scale_x_continuous( n.breaks=9 ) +
    labs( y="Criterion", x="Model Number", title="AIC, BIC, and Deviance", color="" ) +
    theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15),
          plot.title=element_text(size=17), axis.title.x=element_text(size=13),
          axis.title.y=element_text(size=13), legend.position = "top")

grid.arrange(mcfad, aicbicdev, nrow=1)
```

## *Cross Validation*
```{r}
set.seed(1234)
cv.errors <- function( df ){
    df <- data.frame( model=df$model )
    for( i in 1:nrow( df ) ){
        glm.fit <- glm( df$model[i], data=combo.df, family="binomial" )
        df$loocv[i] <- cv.glm( combo.df, glm.fit )$delta[1]
        df$kfcv.5[i] <- cv.glm( combo.df, glm.fit, K=5)$delta[1]
        df$kfcv.10[i] <- cv.glm( combo.df, glm.fit, K=10)$delta[1]
    }
    return( df )
}
error.df <- cv.errors( glm.model.stats )
head(error.df, n=10)

error.df[ which.min(error.df$loocv), ]
error.df[ which.min(error.df$kfcv.5), ]
error.df[ which.min(error.df$kfcv.10), ]

ggplot( data=error.df ) +
    geom_path( aes(x=1:16, y=loocv, colour="LOOCV") ) +
    geom_point( aes(x=1:16, y=loocv, colour="LOOCV") ) +
    geom_path( aes(x=1:16, y=kfcv.5, colour="5-Fold CV") ) +
    geom_point( aes(x=1:16, y=kfcv.5, colour="5-Fold CV") ) +
    geom_path( aes(x=1:16, y=kfcv.10, colour="10-Fold CV") ) +
    geom_point( aes(x=1:16, y=kfcv.10, colour="10-Fold CV") ) +
    theme_light() + scale_y_continuous(n.breaks=10) + scale_x_continuous(n.breaks=16) +
    labs(y="Validation Error Rate", x="Model #", colour="CV Method", title="Validation Error Rates for Each Model") +
    theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15),
          plot.title=element_text(size=17), axis.title.x=element_text(size=13),
          axis.title.y=element_text(size=13), legend.position = "right")
```


## *Test Error Rates*
```{r}
set.seed(1234)

prediction.errors <- function( formula ){
    training.set <- combo.df %>% filter( year != 2022 )
    testing.set <- combo.df %>% filter( year == 2022 )
    mod <- glm( formula, data=training.set, family=binomial)
    pred <- predict( mod, testing.set, type="response" )
    class <- rep( 0, times=nrow(testing.set) )
    class[ pred > 0.5 ] <- 1
    tab <- table( class, testing.set$draft.fac)
    return( tab )
}


prediction.errors( "draft.fac ~ 1 + Wt + forty_yd + bench + shuttle + tackles_solo" )
( error <- (6+1) / 38 )
```

## *ROC Curve*
```{r}
set.seed(1234)
roc.curve <- function( formula ){
    
    training.set <- combo.df %>% filter( year != 2022 )
    testing.set <- combo.df %>% filter( year == 2022 )
    mod <- glm( formula, data=training.set, family=binomial )
    pred <- predict( mod, testing.set, type="response" )
    class <- rep( 0, times=nrow(testing.set) )
    class[ pred > 0.6 ] <- 1

    roc_score <- roc(
        as.factor( class ),
        testing.set$draft.fac )
return( roc_score )
}
roc_data <- roc.curve( "draft.fac ~ 1 + Wt + forty_yd + bench + shuttle + tackles_solo"  )

roc_df <- data.frame(
  FPR = roc_data$specificities,
  TPR = roc_data$sensitivities
)
roc_df$FPR
roc_df$TPR

roc_plot <- ggplot(roc_df, aes(x = FPR, y = TPR)) +
  geom_line() +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", colour="red", alpha=0.5) +
  labs( x = "False Positive Rate (1 - Specificity)",
       y = "True Positive Rate (Sensitivity)",
       subtitle = "draft.fac ~ 1 + Wt + forty_yd + bench + shuttle + tackles_solo") +
    theme_ipsum() +
    annotate( "text", x=0.5, y=0.5, 
              label=paste( "AUC =", round(roc_data$auc, 3)), color="blue", size=4) +
    theme(axis.text.x=element_text(size=15), axis.text.y=element_text(size=15),
          plot.title=element_text(size=17), axis.title.x=element_text(size=13),
          axis.title.y=element_text(size=13), legend.position = "right")
roc_plot
```

\newpage

# **Interpretations**

```{r}
setwd("~/Documents/STSCI 4100")
combo.df <- read_csv("combo.df.csv")[,c(6:13, 17:24, 28, 27)]


final.mod <- glm(draft.fac ~ Wt+forty_yd+bench+shuttle+tackles_solo,
                 data=combo.df, family=binomial)
summary(final.mod)
```
$draft.fac{_i} = 27.9033+0.091(Wt){_i}-7.7742(forty\_yd){_i}+0.0759(bench){_i}-3.492(shuttle){_i}+0.0095(tackles\_solo){_i} + e{_i}$

## *Coefficients and Interpretations*
```{r}

( beta1 <- final.mod$coefficients[2] )
( beta2 <- final.mod$coefficients[3] )
( beta3 <- final.mod$coefficients[4] )
( beta4 <- final.mod$coefficients[5] )
( beta5 <- final.mod$coefficients[6] )



( OR.1 <- exp(beta1) )
( OR.2 <- exp(0.01*beta2) )
( OR.3 <- exp(beta3) )
( OR.4 <- exp(0.01*beta4) )
( OR.5 <- exp(beta5) )

    
    
    

confint(final.mod)


( OR.CI.1 <- c(exp(0.057326753), exp(0.12725880)) )
( OR.CI.2 <- c(exp(0.01*-10.505913203), exp(0.01*-5.25160681)) )
( OR.CI.3 <- c(exp(0.003271339), exp(0.15129353)) )
( OR.CI.4 <- c(exp(0.01*-6.001425515), exp(0.01*-1.06292465)) )
( OR.CI.5 <- c(exp(0.003976453), exp(0.01539862)) )


```